---
title: "Computational Modelling - Assignment 3"
author: "Dana Jensen"
date: "3/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

PRELUDE

```{r}

setwd("C:/Users/danaj/OneDrive/Desktop/COMPUTATIONAL MODELLING/ComputationalModelling")
library(pacman)
p_load(readr,groupdata2,ggplot2,tidyverse,data.table,lmerTest, jpeg, grid, brms, rethinking,gridGraphics)
df = read.csv("Assignment3Data.csv")

```

Multivariate linear models

# In this assignment you will investigate the relation between different aspects of IQ and symptom severity in ASD (as measured by ADOS). The assignment is meant to make you practice on linear models, multiple predictors and interactions. The questions should be answered by focusing on visit 1.

# 1. Assess the relation between symptom severity and IQ (focus on visit 1 and children with ASD) and report the model, a plot of the model, a couple of lines describing the quality of the model and interpreting the results. P.S. Should you scale? P.P.S. Don't forget to motivate your priors. P.P.P.S. At least one plot for results and a plot for quality of each model (here and in the next questions) would be appreciated.

## 1.1. Verbal IQ and ADOS

```{r}

## subset first visit and autistic 
first_visit = subset(df, Visit == 1 & ASD == 1)
## scale and centre
first_visit$ADOS = scale(first_visit$ADOS)
first_visit$VerbalIQ = scale(first_visit$VerbalIQ, center = TRUE)
## run correlation test
cor(first_visit,  method = "pearson")

## motivate prior
mean(first_visit$VerbalIQ) ## we scaled so it's zero

## it makes theoretical sense to change visit, gender, ASD, and ChildID to factors
df$Gender <- as.factor(df$Gender)
df$Visit <- as.factor(df$Visit)
df$ASD <- as.factor(df$ASD)
df$ChildID <- as.factor(df$ChildID)

## make a model
verbal = map(
  alist(
    ADOS ~ dnorm(m ,s),
    m <- a + b*VerbalIQ,
    a ~ dnorm(0, 1), 
    b ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = first_visit)

## plot estimates
m1 <- precis(verbal, corr = T)
plot(m1)

## calculating values for the plot
post1 = extract.samples(verbal) #posterior from samples 
mu.link1 = function(VerbalIQ) post1$a + post1$b*VerbalIQ
VIQ.seq1 = seq(from = min(first_visit$VerbalIQ) , to = max(first_visit$VerbalIQ) , by = 0.1 )
mu1 = sapply(VIQ.seq1 , mu.link1 )
mu.mean1 = apply(mu1 , 2 , mean )
mu.HPDI1 = apply(mu1 , 2 , HPDI , prob=0.89 )
sim.VIQ1 = sim(verbal, data = list(VerbalIQ = VIQ.seq1) )
VIQ.PI1 = apply(sim.VIQ1 , 2 , PI , prob=0.89 )

## plotting posterior
plot( ADOS ~ VerbalIQ , first_visit, col = col.alpha(rangi2,0.5) )
lines( VIQ.seq1 , mu.mean1 ) ## draw MAP line
shade( mu.HPDI1 , VIQ.seq1 ) ## draw HPDI region for line
shade( VIQ.PI1 , VIQ.seq1 ) ## draw PI region for simulated heights

```

## 1.2. Non Verbal IQ and ADOS

```{r}

## scale and centre
first_visit$NonVerbalIQ = scale(first_visit$NonVerbalIQ, center = T)

## make a model
non_verbal = map(
  alist(
    ADOS ~ dnorm(m ,s),
    m <- a + b*NonVerbalIQ,
    a ~ dnorm(0, 1), 
    b ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = first_visit)

## plot estimates
m2 = precis(non_verbal, corr = T)
plot(m2)

#calculating values for the plot
post2 = extract.samples(non_verbal) #posterior from samples 
mu.link2 = function(NonVerbalIQ) post2$a + post2$b*NonVerbalIQ
VIQ.seq2 = seq(from = min(first_visit$NonVerbalIQ) , to = max(first_visit$NonVerbalIQ) , by = 0.1 )
mu2 = sapply(VIQ.seq2 , mu.link2 )
mu.mean2 = apply(mu2 , 2 , mean )
mu.HPDI2 = apply(mu2 , 2 , HPDI , prob=0.89 )
sim.VIQ2 = sim(non_verbal , data = list(NonVerbalIQ = VIQ.seq2) )
VIQ.PI2 = apply(sim.VIQ2 , 2 , PI , prob = 0.89 )

## plotting posterior
plot( ADOS ~ NonVerbalIQ , first_visit, col = col.alpha(rangi2,0.5) )
lines( VIQ.seq2 , mu.mean2 ) ## draw MAP line
shade( mu.HPDI2 , VIQ.seq2 ) ## draw HPDI region for line
shade( VIQ.PI2 , VIQ.seq2 ) ## draw PI region for simulated heights

```

## 1.3. Social IQ and ADOS

```{r}

## scale and center
first_visit$SocialIQ = scale(first_visit$SocialIQ, center = T)

## make a model
social = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b*SocialIQ,
    a ~ dnorm(0, 1), 
    b ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = first_visit)

## plot estimates
m3 = precis(social, corr = T)
plot(m3)

## calculating values for the plot
post3 = extract.samples(social) #posterior from samples 
mu.link3 = function(SocialIQ) post3$a + post3$b*SocialIQ
VIQ.seq3 = seq(from = min(first_visit$SocialIQ) , to = max(first_visit$SocialIQ) , by = 0.1 )
mu3 = sapply(VIQ.seq3 , mu.link3 )
mu.mean3 = apply(mu3 , 2 , mean )
mu.HPDI3 = apply(mu3 , 2 , HPDI , prob = 0.89 )
sim.VIQ3 = sim(social , data = list(SocialIQ = VIQ.seq3) )
VIQ.PI3 = apply(sim.VIQ3 , 2 , PI , prob = 0.89 )

## plotting posterior
plot3 = plot( ADOS ~ SocialIQ , first_visit, col = col.alpha(rangi2,0.5) )
lines( VIQ.seq3 , mu.mean3 ) ## draw MAP line
shade( mu.HPDI3 , VIQ.seq3 ) ## draw HPDI region for line
shade( VIQ.PI3 , VIQ.seq3 ) ## draw PI region for simulated heights

```

# 2. Do the different aspects of IQ account for different portions of the variance in ADOS? 
# 2.1. Does it make sense to have all IQ measures in the same model? First write a few lines answering the question and motivating your answer, including a discussion as to what happens when you put all of them in the same model. Then build a model following your answer. If your answer is "no", you are not free, you still have to answer: are there alternative ways of answering the question?
# 2.2. Build the model, assess its quality, write a few lines interpreting the results.

```{r}

## make a model
e_all_the_above = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*NonVerbalIQ + b3*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    b3 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = first_visit)

## plot estimates
m4 = precis(e_all_the_above, corr = T)
plot(m4)

## plotting posterior
post4 = extract.samples(e_all_the_above) #posterior from samples 

## extract beta values to plot
b1=post4$b1
b2=post4$b2
b3=post4$b3

## layered histogram
ggplot(post4) +
    geom_histogram(aes(b1), fill = "red", alpha = 0.2)+
    geom_histogram(aes(b2), fill = "blue", alpha = 0.2)+
    geom_histogram(aes(b3), fill = "green", alpha = 0.2)

```

# 3. Let's now include also the TD children. Does it make sense to ask whether IQ and ADOS are related? Motivate your answer. In any case, if you wanted to build a model to answer that question, which model would you build? Run the model, assess its quality, write a few lines interpreting the results.

```{r}

## I don't want no scrubs
df = na.omit(df) 

## scale and center
df$ADOS = scale(df$ADOS, center = T)
df$VerbalIQ = scale(df$VerbalIQ, center = T)
df$NonVerbalIQ = scale(df$NonVerbalIQ, center = T)
df$SocialIQ = scale(df$SocialIQ, center = T)

## make a model
typical = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*NonVerbalIQ + b3*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    b3 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = df)

## plot estimates
m5 = precis(typical)
plot(m5)

# Do verbal & non-verbal share variance without social?

## make a model
verbal_non = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*NonVerbalIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = df)

## plot estimates
m6 = precis(verbal_non)
plot(m6)

## make a model
verbal_social = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = df)

## plot estimates
m7 = precis(verbal_social)
plot(m7)

```

# 4. Let's discuss contents:
# 4.1. You have three scores for IQ, do they show shared variance? Is that the same in TD and ASD? What does that tell us about IQ?
# 4.2. You have explored the relation between IQ and ADOS. How do you explain that relation from a cognitive perspective? N.B. You can present alternative hypotheses.

```{r}

## subset data for typically developing
TD = subset(df, Visit == 1 & ASD == 0)

## make a model
typical_all = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*NonVerbalIQ + b3*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    b3 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = TD)

## plotting estimates
m8 = precis(typical_all)
plot(m8)

## make a model
typical_verbal_non = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*NonVerbalIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = TD)

## plot estimates
m9 = precis(typical_verbal_non)
plot(m9)

## make a model
typical_verbal_social = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*VerbalIQ + b2*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = TD)

## plot estimates
m10 = precis(typical_verbal_social)
plot(m10)

## make a model
typical_non_social = map(
  alist(
    ADOS ~ dnorm(m, s),
    m <- a + b1*NonVerbalIQ + b2*SocialIQ,
    a ~ dnorm(0, 1), 
    b1 ~ dnorm(0, 1),
    b2 ~ dnorm(0, 1),
    s ~ dunif(0, 1)
    ) ,
  data = TD)

## plot estimates
m11 = precis(typical_non_social)
plot(m11)

```

END
