---
title: "Eye Tracking"
author: "Blanka Zana"
date: "5 February 2018"
output: html_document
---

 1, data recording (data files (x,y coordinates, pupillary), stimulus files (pictres, onset), auxillary data (EEG or other data collection method, fMRI))
 2, Defining hypothesis
    conceptual
    operational
    
Hypotheses:
1)
C: Visal search patterns are affected by task structure (top-down)
O: - Fixation duration, position (spatial dispersion)
   - Saccades amplitude,amplitude, N, P next
2)
C: More emotionally engaged when involved in interaction (~direction and ostensiveness)
O:- pupil size (time, lighting, in fixations and in saccades?)
  - fixation duration
    

```{r setup}
pacman::p_load(readr,groupdata2,ggplot2,tidyverse,lmerTest,lme4,MuMIn,data.table,jpeg,grid,tidyr)

# Both experiments are in the same files
setwd("C:/Users/danaj/OneDrive/Desktop/COMPUTATIONAL MODELLING/ComputationalModelling")
Samples=read_delim('eyetracking_2018_samples.txt',delim='\t')
Fixations=read_delim('eyetracking_2018_fixations.txt',delim='\t')
Saccades=read_delim('eyetracking_2018_saccades.txt',delim='\t')

```

Loading the clean data V1s
```{r}

sac_V1=read.csv2('SaccadesV1.csv',sep = ",")
samp_V1 = read.csv2('SamplesV1.csv',sep = ",")
fix_V1 = read.csv2('FixationsV1.csv', sep = ",")

log1 = read.csv2('./PupilsLogs/logfile_1_2_f.csv',sep = ",")
log2 = read.csv2('./PupilsLogs/logfile_2_1_f.csv',sep = ",")
log3 = read.csv2('./PupilsLogs/logfile_3_2_f.csv',sep = ",")
log4 = read.csv2('./PupilsLogs/logfile_4_1_F.csv',sep = ",")
log5 = read.csv2('./PupilsLogs/logfile_5_2_m.csv',sep = ",")
log6 = read.csv2('./PupilsLogs/logfile_6_1_m.csv',sep = ",")
all_logs = merge(log1, log2, all = T)
all_logs = merge(all_logs, log3, all = T)
all_logs = merge(all_logs, log4, all = T)
all_logs = merge(all_logs, log5, all = T)
all_logs = merge(all_logs, log6, all = T)

setnames(all_logs,"subject","ParticipantID")
colnames(all_logs)[1] <- "Trial"
all_logs$Trial = all_logs$Trial + 1
logs_sac_V1 = merge(all_logs,sac_V1,all = T)
logs_samp_V1 = merge(all_logs,samp_V1, all = T)
logs_fix_V1 = merge(all_logs,fix_V1, all = T)

logs_sac_V1$SearchOrder = as.numeric(logs_sac_V1$SearchOrder)
logs_sac_V1$Condition[logs_sac_V1$Trial < 6 & logs_sac_V1$SearchOrder == "1"] = "Search"
logs_sac_V1$Condition[logs_sac_V1$Trial > 6 & logs_sac_V1$SearchOrder == "1"] = "Count"
logs_sac_V1$Condition[logs_sac_V1$Trial < 6 & logs_sac_V1$SearchOrder == "2"] = "Count"
logs_sac_V1$Condition[logs_sac_V1$Trial > 6 & logs_sac_V1$SearchOrder == "2"] = "Search"
logs_samp_V1$Condition[logs_samp_V1$Trial < 6 & logs_samp_V1$SearchOrder == "1"] = "Search"
logs_samp_V1$Condition[logs_samp_V1$Trial > 6 & logs_samp_V1$SearchOrder == "1"] = "Count"
logs_samp_V1$Condition[logs_samp_V1$Trial < 6 & logs_samp_V1$SearchOrder == "2"] = "Count"
logs_samp_V1$Condition[logs_samp_V1$Trial > 6 & logs_samp_V1$SearchOrder == "2"] = "Search"
logs_fix_V1$SearchType[logs_fix_V1$Trial < 6 & logs_fix_V1$SearchOrder == "1"] = "Search"
logs_fix_V1$SearchType[logs_fix_V1$Trial > 6 & logs_fix_V1$SearchOrder == "1"] = "Count"
logs_fix_V1$SearchType[logs_fix_V1$Trial < 6 & logs_fix_V1$SearchOrder == "2"] = "Count"
logs_fix_V1$SearchType[logs_fix_V1$Trial > 6 & logs_fix_V1$SearchOrder == "2"] = "Search"
 
logs_sac_V1$DIRECTION [grepl("dir", logs_sac_V1$video)] = "Towards you"
logs_sac_V1$DIRECTION [grepl("div", logs_sac_V1$video)] = "Towards 3rd"
logs_samp_V1$DIRECTION [grepl("dir", logs_samp_V1$video)] = "Towards you"
logs_samp_V1$DIRECTION [grepl("div", logs_samp_V1$video)] = "Towards 3rd"
logs_fix_V1$DIRECTION [grepl("dir", logs_fix_V1$video)] = "Towards you"
logs_fix_V1$DIRECTION [grepl("div", logs_fix_V1$video)] = "Towards 3rd"

#also with ostensiveness
logs_sac_V1$Ostensiveness [grepl("+o", logs_sac_V1$video)] = "Ostensive"
logs_sac_V1$Ostensiveness [grepl("-o", logs_sac_V1$video)] = "Not ostensive"
logs_samp_V1$Ostensiveness [grepl("+o", logs_samp_V1$video)] = "Ostensive"
logs_samp_V1$Ostensiveness [grepl("-o", logs_samp_V1$video)] = "Not ostensive"
logs_fix_V1$Ostensiveness [grepl("+o", logs_fix_V1$video)] = "Ostensive"
logs_fix_V1$Ostensiveness [grepl("-o", logs_fix_V1$video)] = "Not ostensive"

##also with actor gender
logs_sac_V1$ActorGender [grepl("f", logs_sac_V1$video)] = "Female"
logs_sac_V1$ActorGender [grepl("m", logs_sac_V1$video)] = "Male"
logs_samp_V1$ActorGender [grepl("f", logs_samp_V1$video)] = "Female"
logs_samp_V1$ActorGender [grepl("m", logs_samp_V1$video)] = "Male"
logs_fix_V1$ActorGender [grepl("f", logs_fix_V1$video)] = "Female"
logs_fix_V1$ActorGender [grepl("m", logs_fix_V1$video)] = "Male"

```

Cleaning
```{r}

# fixations by tasks
Visual_fix = subset(logs_fix_V1, Task == "VisualSearch")
Social_fix = subset(logs_fix_V1, Task == "SocialEngagement")

# saccades by tasks
Visual_sac = subset(logs_sac_V1, Task == "VisualSearch")
Social_sac = subset(logs_sac_V1, Task =="SocialEngagement")

#sample by tasks
Visual_samp = subset(logs_samp_V1, Task == "VisualSearch")
Social_samp = subset(logs_samp_V1, Task == "SocialEngagement")

Visual_fix$SearchType = as.factor(Visual_fix$SearchType)

```

Visualization 

```{r}

#V2 part
ggplot(Visual_fix, aes(Duration, na.rm = T)) + 
  geom_density() + 
  facet_wrap(~SearchType)

ggplot(logs_sac_V1, aes(MeanVelocity)) + 
  geom_histogram() + 
  facet_wrap(~Task)

ggplot(FixV2, aes(PupilSize, fill = ParticipantID)) + 
  geom_density() + 
  facet_wrap(~Task)

```

VISUAL SEARCH

FIXATION DURATION
```{r}

dammn = glmer(Duration~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(dammn)

duck = glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(duck)

molly = glmer(Duration~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(molly)

```

Cross Validation
```{r}

logs_fix_V1 = read.csv("FixationsV2.csv")

#subset first
search = subset(logs_fix_V1,Task == "VisualSearch")
summary(logs_fix_V1$ParticipantGender[unique(logs_fix_V1$ParticipantID)])
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
search$ParticipantID[search$ParticipantGender=="male"]

folds=4

#add column called "folds"
foldyFixV2=fold(search, folds, id_col = "ParticipantID")
summary(foldyFixV2$.folds)

gmod="glmer(Duration~SerachType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod1="glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod2="glmer(Duration~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"

models=c(gmod,mod1,mod2) 
cross_v=function(numfolds, data, tempmod_string){
  foldyFixV2=fold(search, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldyFixV2, .folds != i) #
    temp_test = subset(foldyFixV2, .folds == i) #
    
    temp_model = glmer(Duration~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldyFixV2, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldyFixV2, temp_model))
  }

try = results_df
try = data.frame(try)
try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)
try = setnames(try,"perf_test_list", "mean_test_rmse" )
```

The best model is duck (the interaction one), so run it on the whole data set.

```{r}
duck = glmer(Duration~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), logs_fix_V1)
summary(duck)

plot(resid(duck))
```

SACCADE AMPLITUDES
```{r}

logs_sac_V1 = read.csv("SaccadesV2.csv")

#subset first
search = subset(logs_sac_V1,Task == "VisualSearch")
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))

```

Cross validation
```{r}
folds=4

#add column called "folds"
foldySacV2=fold(search, folds, id_col = "ParticipantID")
summary(foldySacV2$.folds)

# model strings
gmod="glmer(Amplitude~SerachType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod1="glmer(Amplitude~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
mod2="glmer(Amplitude~SearchType + (1+SearchType |ParticipantID),family = gaussian (link = log), search)"
models=c(gmod,mod1,mod2) 

cross_v=function(numfolds, data, tempmod_string){
  foldySacV2=fold(search, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()
  #r2m=c()
  #r2c=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldySacV2, .folds != i) #
    temp_test = subset(foldySacV2, .folds == i) #
    
    temp_model = glmer(Amplitude~SearchType + Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
    
    #r2_df = as.data.frame(r.squaredGLMM(temp_model)) 
    #r2m = c(r2m,r2_df[1,1])
    #r2c = c(r2c,r2_df[2,1])
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldySacV2, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldySacV2, temp_model))
  }

try = results_df
try = data.frame(try)
try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)
try = setnames(try,"perf_test_list", "mean_test_rmse" )

```

The Best model Amplitude

```{r}

h2  = glmer(Amplitude~SearchType * Trial + (1+SearchType |ParticipantID),family = gaussian (link = log), search)

summary(h2)

```

Just Plots
```{r}

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img <- readJPEG('eyetrackingscripts/foraging/ng090ws.jpg')
g = rasterGrob(img,interpolate=TRUE)

#density
a = ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='6_3_m2' & Trial==6), aes(x = PositionX, y = PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")

a

fin

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img2 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g1 = rasterGrob(img2,interpolate=TRUE)

#density
b = ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='3_1_f1' & Trial==3), aes(x = PositionX, y = 1081 -PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g1, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")

fin

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img4 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g3 = rasterGrob(img4,interpolate=TRUE)

#density
ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='2_2_f2' & Trial==3), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g3, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")

gridExtra::grid.arrange(a,b,c)

plot(b)
par(new = TRUE)
plot(c)
par(new = T)
plot(d)

FixationsV2 = read.csv('FixationsV2.csv')
jet.colors = colorRampPalette(c("#00007F", "blue","#007FFF","cyan","#7FFF7F","yellow","#FF7F00","red","#7F0000"))

img4 <- readJPEG('eyetrackingscripts/foraging/ng049ws.jpg')
g4 = rasterGrob(img4,interpolate=TRUE)

#density
ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='5_1_m2' & Trial==3), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g4, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
d

```

More Plots
```{r}

img6 <- readJPEG('eyetrackingscripts/foraging/ng021ws.jpg')
g6 = rasterGrob(img6,interpolate=TRUE)

ggplot(subset(FixationsV2, Task=='VisualSearch' & ParticipantID=='1_1_f1' & Trial==1), aes(x = PositionX, y = 1081-PositionY)) +
xlim(0,1920) +
ylim(0, 1080) +
annotation_custom(g6, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + #xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf) +
stat_density2d(geom="raster", aes(fill=..density.., alpha=sqrt(sqrt(..density..))), contour=FALSE, n=1000) + 
scale_alpha(range = c(0.1, 0.6)) + scale_fill_gradientn(colours = jet.colors(10), trans="sqrt")
#SCANPATHS
x = 
ggplot(subset(FixationsV2, Task == 'VisualSearch' & ParticipantID=='1_1_f1' & Trial==1), aes(x=PositionX, y= 1081-PositionY, label=Fixation))  +
annotation_custom(g6, xmin=-Inf, xmax=Inf, ymin=-0, ymax=1080) + 
geom_point(size = 10, alpha = 0.8, color = "magenta") +
geom_path(size = 1, alpha = 0.3) +
geom_text(aes(label = Fixation, size = 5)) 

x

#Pupil size change over time plot
SamplesV2 = read.csv("SamplesV2.csv")

ggplot(subset(SamplesV2, Task =="SocialEngagement"), aes(TrialTime, PupilSize, colour = Ostension, na.rm = T)) +geom_smooth() + facet_grid(~Directionality)

ggplot(search, aes(Trial,Duration, colour = SearchType, na.rm = T)) + geom_smooth() #facet_grid(~SearchType)
search$ParticipantID = as.numeric(as.factor(as.character(search$ParticipantID)))
search$ParticipantID = as.factor(search$ParticipantID)
ggplot(search, aes(Trial,Duration, colour = ParticipantID, na.rm = T)) + geom_point() + facet_grid(~SearchType)

ggplot(subset(search, ParticipantID=="4"), aes(Stimulus, Duration)) + geom_point()+facet_grid(~SearchType)

ggplot(search,aes(Amplitude,fill = SearchType, colour = SearchType)) + geom_density() + facet_wrap(~SearchType)

search$Trial = as.factor(search$Trial)
ggplot(search, aes(Trial, Amplitude, colour = SearchType)) +geom_smooth() + facet_grid(~Directionality)

```

SOCIAL ENGAGEMENT

1) what we wanna look at
  Pupil size ~ Ost + DIR + Time +(1+Ost*DIR|Part)
  
```{r}
SamplesV2 = read.csv("SamplesV2.csv")

#subset
social = subset(SamplesV2,Task == "SocialEngagement")
summary(logs_fix_V1$ParticipantGender[unique(logs_fix_V1$ParticipantID)])
social$ParticipantID = as.numeric(as.factor(as.character(social$ParticipantID)))

#identify outliers need to be removed
ggplot(social,aes(ParticipantID, PupilSize, colour = ParticipantID)) + geom_point()

#models
social = subset(social, PupilSize > 0)
social$ParticipantID = factor(social$ParticipantID)
social$PupilSize = scale(social$PupilSize, center = TRUE)

mom = glmer(PupilSize~Ostension * Directionality * Trial + (1+Ostension + Directionality |ParticipantID), family = gaussian (link = log), social)

dad = glmer(PupilSize~Ostensiveness + Directionality + Trial + (1+Ostensiveness + Directionality |ParticipantID), family = gaussian (link = log), social)

model1 = glmer(PupilSize ~ Ostension + Directionality + TrialTime, (1 + Ostension + Directionality | ParticipantID), family = gaussian (link = log), social)

model2 = glmer(PupilSize ~ Ostension * Directionality * TrialTime + (1 + Ostension + Directionality | ParticipantID + Trial), family = gaussian (link = log),social)

model3 = glmer(PupilSize ~ Ostension + Directionality + (1 + Ostension + Directionality | ParticipantID + Trial), family = gaussian (link = log),social)

model4 = glmer(PupilSize ~ Ostension * Directionality + (1+Ostension + Directionality | ParticipantID + Trial), family = gaussian (link = log),social)

summary(mom)
summary(dad)
summary(model1)
summary(model2)
summary(model3)
summary(model4)

```

bar plot
```{r}
#subset
FixV2 = read.csv("FixationsV2.csv")
social = subset(FixV2,Task == "SocialEngagement")
social$ParticipantID = as.numeric(as.factor(as.character(social$ParticipantID)))
# it needed this for some reason
social$PupilSize <- as.vector(social$PupilSize)


ggplot(social, aes(Ostension,PupilSize, fill = Ostension)) +
  geom_bar(stat = "summary",fun.y = mean) + 
  geom_errorbar(stat = "summary",fun.data = mean_se, width = 0.4)+
    facet_grid(~ Directionality)

ggplot(social, aes(Directionality,PupilSize, fill = Directionality)) +
  geom_bar(stat = "summary",fun.y = mean) + 
  geom_errorbar(stat = "summary",fun.data = mean_se, width = 0.4)+
    facet_grid(~ Ostension)


```

Another model
```{r}

b = glmer(PupilSize ~ Ostension + Directionality + Trial + (1 + Directionality |ParticipantID) + (1 + Ostension | ParticipantID), family = gaussian (link = log), social)
summary(b)

```

Cross validation
```{r}

folds=4

#add column called "folds"
foldysocial=fold(social, folds, id_col = "ParticipantID")
summary(foldySampV2$.folds)

gmod="glmer(PupilSize~Ostension + Directionality + Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)"
mod1="glmer(PupilSize~Ostension * Directionality * Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"
mod2="glmer(PupilSize~Ostension + Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"
mod3="glmer(PupilSize~Ostension * Directionality + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log),social)"
models=c(gmod,mod1,mod2,mod3) 

cross_v=function(numfolds, data, tempmod_string){
  foldysocial=fold(social, folds, id_col = "ParticipantID")
  perf_test_list=c() #Create variables
  perf_train_list=c()
  #r2m=c()
  #r2c=c()

  for(i in seq(numfolds)){
    temp_train = subset(foldysocial, .folds != i) #
    temp_test = subset(foldysocial, .folds == i) #
    
    temp_model = glmer(PupilSize~Ostension + Directionality + Trial + (1+Ostension + Directionality |ParticipantID),family = gaussian (link = log), social)
  
    pred_test=predict(temp_model, temp_test, allow.new.levels=T) #
    perf_test=Metrics::rmse(temp_test$Duration, pred_test) #
    perf_test_list=c(perf_test_list, perf_test) #
    pred_train=predict(temp_model, temp_train, allow.new.levels=T) #
    perf_train=Metrics::rmse(temp_train$Duration, pred_train) #
    perf_train_list=c(perf_train_list, perf_train) #
    
  }
  
    perf_df= data.frame(perf_test_list, perf_train_list, temp_model=tempmod_string)
  
}

for(temp_model in models) 
  if (temp_model == models[1]){
    results_df=cross_v(4, foldysocial, temp_model)
   }else{
   results_df = rbind(results_df, cross_v(4, foldysocial, temp_model))
  }


try = results_df
try = data.frame(try)
try = group_by(try, temp_model) %>%
  summarise_each(funs(mean(. , na.rm= T)), perf_test_list)
try = setnames(try,"perf_test_list", "mean_test_rmse" )
```
  

