---
title: "Computational Modeling - Assignment 2 Part 1"
author: "Dana Jensen"
date: "2/19/2017"
output: html_document
---

PRELUDE

```{r}

setwd("C:/Users/danaj/OneDrive/Desktop/COMPUTATIONAL MODELLING/ComputationalModelling")
library(pacman)
p_load(coda, mvtnorm, devtools, rethinking, brms, patchwork, gridGraphics)
# devtools::install_github("thomasp85/patchwork", force = T)

```

# You want to assess your teachers' knowledge of cognitive science. "These guys are a bunch of drama(turgist) queens, mindless philosophers, chattering communication people and Russian spies. Do they really know CogSci?", you think.

# To keep things simple (your teachers should not be faced with too complicated things):
# - You created a pool of equally challenging questions on CogSci
# - Each question can be answered correctly or not (we don't allow partially correct answers, to make our life simpler).
# - Knowledge of CogSci can be measured on a scale from 0 (negative knowledge, all answers wrong) through 0.5 (random chance) to 1 (awesome CogSci superpowers)

# This is the data:
# - Riccardo: 3 correct answers out of 6 questions
# - Kristian: 2 correct answers out of 2 questions (then he gets bored)
# - Josh: 160 correct answers out of 198 questions (Josh never gets bored)
# - Mikkel: 66 correct answers out of 132 questions

```{r}

## load data
data <- data.frame(
  Correct = c(3,2,160,66),
  Questions = c(6,2,198,132),
  Teacher = c("RF","KT","JS","MW"))

```

1. What's Riccardo's estimated knowledge of CogSci? What is the probability he knows more than chance (0.5) [try figuring this out. if you can't peek into chapters 3.1 and 3.2 and/or the slides]?
- First implement a grid approximation (hint check paragraph 2.4.1!) with a uniform prior, calculate the posterior and plot the results

```{r}

dens <- 100 ## density
p_grid <- seq( from = 0 , to = 1 , length.out = dens ) ## define grid
prior <- rep( 1 , dens ) ## define prior
likelihood <- dbinom( 6 , size = 9 , prob = p_grid ) ## compute likelihood at each value in grid
unstd.posterior <- likelihood * prior ## compute product of likelihood and prior
posterior <- unstd.posterior / sum(unstd.posterior) ## standardize the posterior, so it sums to 1

## make a plot
temp_df<- data.frame(p_grid = p_grid, posterior = posterior)
ggplot(temp_df, aes(p_grid, posterior))+
  geom_line()+
  labs(x = "Score", y = "Probability", title = "Riccardo's Uninformed Posterior")

```

- Then implement a quadratic approximation (hint check paragraph 2.4.2!).
- N.B. for the rest of the exercise just keep using the grid approximation (we'll move to quadratic approximations in two classes)

```{r}

## make a model
cs.qa = map(
  alist(
    c ~ dbinom(6,p), ## correct answers predicted by # observations and true #
    p ~ dunif(0,1) ## uniform prior (mean 0, sd 1)
    ) ,
  data = list(c = 3)) ## the observed correct answers

## information about uninformed posterior
precis(cs.qa)

## sampling from posterior distribution
dummy <- rbinom( 100 , size = 6 , prob = 0.5 )
simplehist( dummy , main = "Riccardo Dummy Data", xlab = "Answers Correct", ylab = "Probability" )

```

2. Estimate all the teachers' knowledge of CogSci. Who's best? Use grid approximation. Comment on the posteriors of Riccardo and Mikkel.

```{r}

## uninformed prior
prior <- rep( 1 , dens )
temp_df <- data.frame(p_grid = p_grid, prior = prior)
ggplot(temp_df, aes(p_grid, prior))+
  geom_line()+
  labs(x = "Score", y = "Probability", title = "Uniform Prior")

## making uninformed posterior
teachers <- c("RF","KT","JS","MW")
for (teacher in teachers){
  loop_data <- subset(data, Teacher == teacher ) ## data for one teacher only  
  dens <- 1000 ## amount of points to plot  
  p_grid <- seq( from = 0 , to = 1 , length.out = dens ) ## define grid
  prior <- rep( 1 , dens ) ## define prior
  likelihood <- dbinom(loop_data$Correct , size = loop_data$Questions , prob = p_grid )## compute likelihood at each value in grid
  unstd.posterior <- likelihood * prior ## compute product of likelihood and prior
  posterior <- unstd.posterior / sum(unstd.posterior) ## standardize the posterior, so it sums to 1

## make plot
  temp_df <- data.frame(p_grid = p_grid, posterior = posterior)
  temp <- ggplot(temp_df, aes(p_grid, posterior))+
   geom_line()+
   labs(x = "Score", y = "Probability")
  # temp <- grab_grob() ## grab plot and save to variable  
   assign(paste(teacher, "Uninformed_Posterior", sep = "_"), temp)
}

```

2a. Produce plots of the prior, and posterior for each teacher.

```{r}

## display all teachers
gridExtra::grid.arrange(JS_Uninformed_Posterior , RF_Uninformed_Posterior, KT_Uninformed_Posterior, MW_Uninformed_Posterior )

```

3. Change the prior. Given your teachers have all CogSci jobs, you should start with a higher appreciation of their knowledge: the prior is a normal distribution with a mean of 0.8 and a standard deviation of 0.2. Do the results change (and if so how)?

```{r}

## informed prior
dens <- 100
p_grid <- seq( from = 0 , to = 1 , length.out= dens )
prior <- dnorm(p_grid,0.8,0.2)
temp_df<- data.frame(p_grid = p_grid, prior = prior)
ggplot(temp_df, aes(p_grid, prior))+
  geom_line()+
  labs(x = "Score", y = "Probability", title = "Informed Prior")

## making informed posterior
for (teacher in teachers){
  loop_data <- subset(data, Teacher == teacher )
  dens <- 1000
  p_grid <- seq( from = 0 , to = 1 , length.out = dens )
  prior = dnorm(p_grid,0.8,0.2)
  likelihood <- dbinom(loop_data$Correct , size = loop_data$Questions , prob = p_grid)
  unstd.posterior <- likelihood * prior
  posterior <- unstd.posterior / sum(unstd.posterior)

  ## make plot  
  temp_df <- data.frame(p_grid = p_grid, posterior = posterior)
  temp <-ggplot(temp_df, aes(p_grid, posterior))+
   geom_line()
 assign(paste(teacher, "informed", sep = "_"), temp)
}

```

3a. Produce plots of the prior and posterior for each teacher.

```{r}

## informed 
gridExtra::grid.arrange(JS_informed , RF_informed, KT_informed, MW_informed )

```

4. You go back to your teachers and collect more data (multiply the previous numbers by 100). Calculate their knowledge with both a uniform prior and a normal prior with a mean of 0.8 and a standard deviation of 0.2. Do you still see a difference between the results? Why?

```{r}

## multiplying values by 100
data$Correct <- data$Correct * 100
data$Questions <- data$Questions * 100

## making uninformed posterior 
for (teacher in teachers){
  loop_data <- subset(data, Teacher == teacher )
  dens <- 1000
  p_grid <- seq( from = 0 , to = 1 , length.out= dens )
  prior <- rep( 1 , dens)
  likelihood <- dbinom(loop_data$Correct , size = loop_data$Questions , prob = p_grid)
  unstd.posterior <- likelihood * prior
  posterior <- unstd.posterior / sum(unstd.posterior)
  temp_df <- data.frame(p_grid = p_grid, posterior = posterior)
  temp <- ggplot(temp_df, aes(p_grid, posterior))+
   geom_line()
 assign(paste(teacher, "uninformed", sep = "_"), temp)
}

## uninformed
gridExtra::grid.arrange(JS_uninformed , RF_uninformed, KT_uninformed, MW_uninformed )

## making informed posterior
for (teacher in teachers){
  loop_data <- subset(data, Teacher == teacher )
  dens <- 1000
  p_grid <- seq( from = 0 , to = 1 , length.out = dens )
  prior <- dnorm(p_grid,0.8,0.2)
  likelihood <- dbinom(loop_data$Correct , size = loop_data$Questions , prob = p_grid)
  unstd.posterior <- likelihood * prior
  posterior <- unstd.posterior / sum(unstd.posterior)

  ## making a plot
  temp_df <- data.frame(p_grid = p_grid, posterior = posterior)
  temp <- ggplot(temp_df, aes(p_grid, posterior))+
   geom_line()+
   labs(x = "Score", y = "Probability")
 assign(paste(teacher, "informed", sep = "_"), temp)
}

## informed 
gridExtra::grid.arrange(JS_informed , RF_informed, KT_informed, MW_informed )

## calculation of distribution statistics
for (teacher in teachers){ 
  ## uninformed
  loop_data <- subset(data, Teacher == teacher)
  cs.qa = map(
    alist(
      c ~ dbinom(loop_data$Questions,p), 
      p ~ dunif(0,1) 
    ) ,
    data = list(c = loop_data$Correct)) 
  output <- precis(cs.qa)
  print(output)
  ## informed
  cs.qa = map(
    alist(
      c ~ dbinom(loop_data$Questions,p), 
      p ~ dunif(0.8,0.2) 
    ) ,
    data = list(c = loop_data$Correct)) 
  output <- precis(cs.qa)
  print(output)
}

```

5. Imagine you're a skeptic and think your teachers do not know anything about CogSci, given the content of their classes. How would you operationalize that belief?

```{r}

dens <- 1000
p_grid <- seq( from = 0 , to = 1 , length.out = dens )
prior = pnorm(p_grid, mean = 0.5, sd = 0.1, lower.tail = FALSE, log.p = FALSE)

temp_df <- data.frame(p_grid = p_grid, prior = prior)
ggplot(temp_df, aes(p_grid, prior))+
   geom_line()+
   labs(x = "Score", y = "Probability", title = "Skeptical Prior")

```

6. Optional question: Can you estimate the difference between Riccardo's estimated knowledge and that of each of the other teachers? Would you deem it credible (that is, would you believe that it is actually different)?

```{r}

## Riccardo
R_PositiveModel <- brm(Correct|trials(Questions)~1, data = subset(data,Teacher == "RF"), prior = prior("normal(0.8,0.2)", class = "Intercept"), family = 'binomial')

## Kristian
K_PositiveModel <- brm(Correct|trials(Questions)~1, data = subset(data,Teacher == "KT"), prior = prior("normal(0.8,0.2)", class = "Intercept"), family = 'binomial')

## Joshua
J_PositiveModel <- brm(Correct|trials(Questions)~1, data = subset(data,Teacher == "JS"), prior = prior("normal(0.8,0.2)", class = "Intercept"), family = 'binomial')

## Mikkel
M_PositiveModel <- brm(Correct|trials(Questions)~1, data = subset(data,Teacher == "MW"), prior = prior("normal(0.8,0.2)", class = "Intercept"), family = 'binomial')

plot(R_PositiveModel)
plot(K_PositiveModel)
plot(J_PositiveModel)
plot(M_PositiveModel)

```

7. Bonus knowledge: all the stuff we have done can be implemented in a lme4-like fashion using the brms package. Here is an example.

```{r}

FlatModel <- brm(Correct|trials(Questions)~1, data = subset(data,Teacher == "RF"), prior = prior("uniform(0,1)", class = "Intercept"), family = 'binomial')
plot(FlatModel)
temp <- grab_grob()
assign("Flat", temp)

PositiveModel <- brm(Correct|trials(Questions)~1, data=subset(data,Teacher == "RF"), prior = prior("normal(0.8,0.2)", class = "Intercept"), family = 'binomial')
plot(PositiveModel)
temp <- grab_grob()
assign("Positive", temp)

SkepticalModel <- brm(Correct|trials(Questions)~1,data = subset(data,Teacher=="RF"), prior = prior("normal(0.5,0.01)", class = "Intercept"), family = 'binomial')
plot(SkepticalModel)
temp <- grab_grob()
assign("Skeptical", temp)

gridExtra::grid.arrange(FlatModel, PositiveModel, SkepticalModel)

```

If you dare, try to tweak the data and model to test two hypotheses:
- Is Kristian different from Josh?
- Is Josh different from chance?

```{r}

## kristian
k = map(
  alist(
    c ~ dbinom(2,p), ## correct answers predicted by # observations and true #
    p ~ dunif(0,1) ## uniform prior
  ) ,
  data = list(c = 2)) ## the observed correct answers

precis(k)

## joshua
j = map(
  alist(
    c ~ dbinom(198,p), ## correct answers predicted by # observations and true #
    p ~ dunif(0,1) ## uniform prior
  ) ,
  data = list(c = 160)) ## the observed correct answers

precis(j)

```

END
