---
title: "Computational Modelling - Assignment 4"
author: "Dana Jensen"
date: "3/16/2018"
output: html_document
---

PRELUDE

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

setwd("C:/Users/danaj/OneDrive/Desktop/COMPUTATIONAL MODELLING/ComputationalModelling")
library(pacman)
p_load(metafor,lme4,brms, tidyverse, readxl, rethinking, data.table)

## only need data1 for first question
data1 <- read_excel("Assignment4MetaData.xlsx")
## data2 <- read_excel("Assignment4PitchDatav2.xlsx")

## these are the already cleaned, scaled, and centered data, use these for the rest
SchizData <- read.csv("SchizData.csv")
MetaAnalysis <- read.csv("MetaAnalysis.csv")

```

Step 1: Reproduce the meta-analysis of pitch sd from previous studies of voice in schizophrenia
# - the data is available as Assignment4MetaData.xlsx
# - Effect size (cohen's d), sd and variance are already calculated (you're welcome!)
# - Since we're only interested in getting a meta-analytic effect size, let's take a shortcut and use bromance magic (brms): https://mvuorre.github.io/post/2016/2016-09-29-bayesian-meta-analysis/

```{r}

## NOTE: "mean standard deviation between sz and hc is X"

M <- brm(MeanES | se(SdES) ~ 1 + (1|StudyRef), data = data1 , iter = 2000, cores = 2, chain = 2)

summary(M)
plot(M)

```

Step 2: Prepare the pitch SD data from last year
# - the data is available as Assignment4PitchData.csv (thanks Celine)
# - We do not know how to build random effects, yet. So we need to simplify the dataset to avoid interdependence between datapoints: How? 
##  NOTE: take mean for every participant so there is one datapoint
# - Also, let's standardize the data, so that they are compatible with our meta-analytic prior (Cohen's d (effect size) is measured in SDs).
##  NOTE: centre and scale

```{r}

## take mean for each participant
## diagnosis seems to change for some participants?
diagnosis = aggregate(data2[,2], by = list(data2$ID), FUN = median)
StudyID = aggregate(data2[,3], by = list(data2$ID), FUN = median)
PitchMean = aggregate(data2[,6], by = list(data2$ID), FUN = mean)
PitchSD = aggregate(data2[,7], by = list(data2$ID), FUN = mean)
ID = unique(data2$ID)
temp1 <- data.frame(ID = ID, PitchMean = PitchMean$PitchMean, PitchSD = PitchSD$PitchSD, ID = PitchMean$Group.1, diagnosis = diagnosis, StudyID = StudyID)

## making df of participants with one datapoint each
temp1 <- select(temp1, ID, PitchMean, PitchSD, diagnosis.diagnosis, StudyID.studynr)
setnames(temp1, "diagnosis.diagnosis", "diagnosis")
setnames(temp1, "StudyID.studynr", "StudyID")

## making df of meta analysis with only relevant columns
temp2 <- select(data1, "StudyID", "PITCH_F0_HC_M",
"PITCH_F0_HC_SD","PITCH_F0_SZ_M","PITCH_F0_SZ_SD","PITCH_F0SD_HC_M","PITCH_F0SD_HC_SD","PITCH_F0SD_SZ_M","PITCH_F0SD_SZ_SD","SdES", "MeanES")

## scale and centre
## final, clean dataset
temp1$PitchMean <- scale(temp1$PitchMean)
temp1$PitchSD <- scale(temp1$PitchSD)
SchizData <- temp1
write.csv(SchizData, file = "SchizData.csv", row.names = FALSE)

## final, clean dataset
temp3 <- select(temp2,"PITCH_F0_HC_M","PITCH_F0_HC_SD","PITCH_F0_SZ_M","PITCH_F0_SZ_SD","PITCH_F0SD_HC_M","PITCH_F0SD_HC_SD","PITCH_F0SD_SZ_M","PITCH_F0SD_SZ_SD","SdES", "MeanES")
temp3 <- scale(temp3)
temp4 <- select(temp2, StudyID)
MetaAnalysis <- cbind(temp4, temp3)
write.csv(MetaAnalysis, file = "MetaAnalysis.csv", row.names = FALSE)

```

Step 3: Build a regression model predicting Pitch SD from Diagnosis.
# - how is the outcome distributed? (likelihood function)
# - how are the parameters of the likelihood distribution distributed? Which predictors should they be conditioned on?
# - use a skeptical/conservative prior for the effects of diagnosis. Remember you'll need to motivate it.
# - Describe and plot the estimates. Evaluate model quality

```{r}

## do we use brm or rethinking?
m1 <- brm(PitchSD ~ 1 + diagnosis + (1|StudyID), data = SchizData, warmup = 2000, iter = 5000, cores = 2, chain = 2)

SchizData$diagnosis <- as.numeric(SchizData$diagnosis)

## but then how to do random effects?
m1 = map(
  alist(
    PitchSD ~ dnorm(m ,s),
    m <- a + b*diagnosis,
    a ~ dnorm(0,1), 
    b ~ dnorm(0,0.2),
    s ~ dcauchy(0,2)
    ) ,
  data= SchizData)

model1=precis(m1, corr = T)
model1
plotm1<-plot(model1)

```

Step 4: Now re-run the model with the meta-analytic prior
# - Describe and plot the estimates. Evaluate model quality

```{r}

## now we have to use the numbers from the 1st model
### intercept: -0.6
### SE(INT): 0.27
### SD(INT): 0.76
### SE(SD(INT)): 0.28

SchizData$diagnosis=as.numeric(SchizData$diagnosis)
m2 = map(
  alist(
    PitchSD ~ dnorm(m ,s),
    m <- a + b*diagnosis,
    a ~ dnorm(0,1), 
    b ~ dnorm(0.76,0.27),
    s ~ dcauchy(0,2)
    ) ,
  data= SchizData)

model2 = precis(m2, corr = T)
model2
plotm2 <- plot(model2)

```

Step 5: Compare the models
# - Plot priors and posteriors of the diagnosis effect in both models
# - Compare posteriors between the two models
# - Compare their relative distance from truth (WAIC)
# - Discuss how they compare and whether any of them is best.

```{r}
## run comparison (WAIC)
models = compare(m1, m2)
plot(models)

## plot priors and posteriors
## prior
plot(dnorm(0,1))
## posterior
post1 = extract.samples(m1)
dens(post1$b)

## prior
plot(dnorm(0,0.27))
## posterior
post2 = extract.samples(m2)
dens(post2$b)

```

END
